---
title: "resolver"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{resolver}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
params:
  resolve: "y"
  selection: 1
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE}
library(resolver)
library(dplyr)
```

The `resolver` function is intended to join multiple datasets with key columns that don't quite match up. To resolve these messy joins, `resolver` takes the `joiner` argument to indicate keys. It also allows for inclusion of a `helper` argument used during interactive resolution of join conflicts, and a `joiners2` argument to attempt a second set of joins on a second series of key columns. Finally, `resolver` uses the `cache` and `cache_loc` arguments to facilitate inclusion in workflows without needing to interact with `resolver` every time a script is run.

```{r data}
data("taxonomy")
data("avonet")
data("eltontraits")
data("nest_heights")
```

Because `resolver` was created to join taxonomic databases (although it works with other types of data too), it pairs well with the `taxadb` package to provide a second of set of keys to join on.

```{r taxadb, warning = FALSE, message = FALSE}
library(taxadb)

taxonomy <- taxonomy %>% mutate(id = get_ids(scientific_name))
  avonet <- avonet %>% mutate(id = get_ids(Species2))
  eltontraits <- eltontraits %>% mutate(id = get_ids(Scientific))
  nest_heights <- nest_heights %>% mutate(id = get_ids(scientific_name))
```

`resolver` will join these four databases together, then query the user to manually clarify unresolved joins. The function returns a list of the joined databases and the crosswalk used to resolve conflicts.

```{r join, warning = FALSE}
joined_dbs <- resolver(
  databases = list(taxonomy, avonet, eltontraits, nest_heights),
  joiners = list("common_name", "common_name", "English", "common_name"),
  helpers = list("scientific_name","Species2","Scientific","scientific_name"),
  joiners2 = list("id", "id", "id", "id")
)
```

This vignette barely demonstrates the functionality of `resolver`, but provides a good starting place! Unfortunately, I can't demonstrate the interactive element of `resolver` in R markdown. Let me know if you have additional questions.

...and here is the output!

```{r output}
print(joined_dbs)
```
